Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2019-05-14 awipev-CO2.Rmd
updated scrptfor Poster

#plot for POSTER june 2019
#plot of S/T
poster_temp <- ggplot(data = d_all%>%dplyr::filter(temp_fb<10 ), aes(x=datetime,y=temp_fb)) +
  geom_point(col="blue", size=0.5 )+
  labs(x = "Time", y="Temperature (°C)") +
  scale_x_datetime(date_minor_breaks ="1 month")+
  theme_bw() + theme(legend.position="bottom",legend.title = element_blank())
print(poster_temp)
ggsave(paste0("figures/poster_temp.png"), width= 30, height=10, poster_temp, units="cm")

poster_sal <- ggplot(data = d_all%>%dplyr::filter(sal_fb>30 ), aes(x=datetime,y=sal_fb)) +
  geom_point(col="blue", size=0.5 )+
  labs(x = "Time", y="Salinity (PSU)") +
  scale_x_datetime(date_minor_breaks ="1 month")+
  theme_bw() + theme(legend.position="bottom",legend.title = element_blank())
print(poster_sal)
ggsave(paste0("figures/poster_sal.png"), width= 30, height=10, poster_sal, units="cm")

@@

at_s <- ggplot(d_all_at_discrete,aes(x=sal_fb, y= at, label = month))+
  geom_text( aes(color=factor(month))) +
  scale_color_discrete(guide="none")+
    labs(x="Salinity", y="Discrete TA", color = "Months") +  
    theme(plot.title = element_text(size=7))  +
    stat_smooth(method = "lm", col = "black") +
    labs(title = paste("Discrete TA vs Salinity", "\nAdj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                       "; Intercept =",signif(fit$coef[[1]],5 ),
                       "; Slope =",signif(fit$coef[[2]], 5),
                       "; P =",signif(summary(fit)$coef[2,4], 5))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + theme_bw()

ggsave(paste0("figures/Discrete_TA_salinity_AWIPEV.png"), at_s, width=15, height =10, units="cm")

@@

#plot for POSTER june 2019
#plot of TA calculated from S + discrete
p_at_sal <- ggplot(data = d_all%>%dplyr::filter(at_calc > 2000), aes(x=datetime,y=at_calc,col="TA calculated from salinity") ) +
  geom_point(col="blue", size=0.5 )+
  geom_point(aes(y=at, fill= "Reference measured samples"), col="red") +
  labs(x = "Time", y = "Calculated TA from salinity (µmoles/kg)") +
  scale_x_datetime(date_minor_breaks ="1 month")+
  theme_bw() + theme(legend.position="bottom",legend.title = element_blank())
print(p_at_sal)
ggsave(paste0("figures/poster_at_sal.png"), width= 30, height=10, p_at_sal, units="cm")

@@

#plot for POSTER june 2019
#plot of TA VS calculated
poster_at_atcal <- ggplot(data = at_nov_2018%>%dplyr::filter(at_calc > 2000), aes(x=at_calc,y=AT_filtered_despike,col="TA calculated from salinity") ) +
  geom_point(col="blue", size=0.5 )+
  labs(x = "Calculated TA", y = "Calculated TA from salinity (µmoles/kg)") +
  theme_bw() + theme(legend.position="bottom",legend.title = element_blank())
print(poster_at_atcal)
ggsave(paste0("figures/poster_at_atcal.png"), width= 30, height=10, poster_at_atcal, units="cm")
```

@@

#plot for POSTER june 2019
#plot of pCO2
poster_pco2 <- ggplot( ) +
  geom_point(data=d_all%>%dplyr::filter(pco2_contros > 150 & pco2_contros < 410), aes(x=datetime, y= pco2_contros,col="blue"), col="blue",size=0.5 ) +
  geom_point(data=d_all, aes(x=datetime, y=pco2calc, fill="Calculated from AT/CT"), col="red" )+
  labs(x = "Time", y = expression(~italic(p)~CO[2]~"(µatm)")) +
  theme_bw() + theme(legend.position="bottom",legend.title = element_blank())
print(poster_pco2)
ggsave(paste0("figures/poster_pco2.png"), width= 30, height=10, poster_pco2, units="cm")
    ```

@@

#plot for POSTER june 2019
#plot of pH seafet
poster_ph <- ggplot( ) +
  geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y= pHint_tot_sf,col="blue"), col="blue",size=0.5 , rm.na=TRUE) +
  geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_seafet_temp_field, fill="Reference measured samples"), col="red" )+
  labs(x = "Time", y = expression(pH[T]~seaFET)) +
  theme_bw() + theme(legend.position="bottom",legend.title = element_blank())

print(poster_ph)
ggsave(paste0("figures/poster_ph.png"), width= 30, height=10, poster_ph, units="cm")

# RANGE of pH
d_all<- d_all%>%
  dplyr::mutate(year = year(datetime))
range <- tbl_df(
  d_all %>%
  group_by(date=as.Date(datetime), month=month(datetime, label=TRUE), year=year(datetime)) %>%
  summarize(pH_range = max(pHint_tot_sf) - min(pHint_tot_sf))
)
quant <- quantile(range$pH_range, probs =c(2.5/100, 97.5/100), na.rm =TRUE)

# Per month
range_month <-
  range %>%
  group_by(Month = month(date, label=TRUE, abbr=FALSE)) %>%
  summarize(pH_range_month = mean(pH_range, na.rm=TRUE))

size_point <- 0.4 # size of data points
plot_range_sf <-  
  ggplot(data=range, aes(x = as.factor(month), y = pH_range)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  labs(y =expression(paste(pH[T], " range seaFET")), x=NULL, title=NULL) +
  Mytheme() +
  theme(panel.grid.major.x = element_blank())
print(plot_range_sf)
ggsave(paste0("figures/plot_range_sf.png"), width= 30, height=10, plot_range_sf, units="cm")

@@

#plot for POSTER june 2019
#plot of pH durafet
poster_dur <- ggplot( ) +
  geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y= pH_durafet_corrected,col="blue"), col="blue",size=0.5 , rm.na=TRUE) +
  geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_durafet_temp_field, fill="Reference measured samples"), col="red" )+
  labs(x = "Time", y = expression(pH[T]~durafet)) +
  theme_bw() + theme(legend.position="bottom",legend.title = element_blank())

print(poster_dur)
ggsave(paste0("figures/poster_dur.png"), width= 30, height=10, poster_dur, units="cm")

# RANGE of pH
range_dur <- tbl_df(
  d_all %>%
  group_by(date=as.Date(datetime), month=month(datetime, label=TRUE), year=year(datetime)) %>%
  summarize(pH_range = max(pH_durafet_corrected) - min(pH_durafet_corrected))
)
quant <- quantile(range_dur$pH_range, probs =c(2.5/100, 97.5/100), na.rm =TRUE)

# Per month
range_month <-
  range_dur %>%
  group_by(Month = month(date, label=TRUE, abbr=FALSE)) %>%
  summarize(pH_range_month = mean(pH_range, na.rm=TRUE))

size_point <- 0.4 # size of data points
plot_range_dur <-  
  ggplot(data=range_dur, aes(x = as.factor(month), y = pH_range)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  labs(y =expression(paste(pH[T], " range durafet")), x=NULL, title=NULL) +
  Mytheme() +
  theme(panel.grid.major.x = element_blank())
print(plot_range_dur)
ggsave(paste0("figures/plot_range_dur.png"), width= 30, height=10, plot_range_dur, units="cm")
```
The average offset between durafet and references (spectro) data is `r average_offset_dur` pH unit (sd = `r sd_offset_dur`, n = `r n_offset_dur`).

>>>>

# #plot for POSTER june 2019
# #plot of S/T
poster_temp <- ggplot(data = d_all%>%dplyr::filter(temp_fb<10 &sal_fb>30 )) + geom_point(aes(x=datetime,y=temp_fb),col="blue", size=0.5) +
  geom_point(aes(x=datetime,y=sal_fb/5),col="red", size=0.5 )+
  labs(x = "Time", y="Temperature (°C)") +
  scale_x_datetime(date_minor_breaks ="1 month")+
  theme_bw() + theme(legend.position="bottom",legend.title = element_blank())+
  scale_y_continuous(sec.axis = sec_axis(~.*5, name = "Salinity (PSU)"))
print(poster_temp)

png("poster_sal_temp.png", width= 1100, height=600)
par(mar=c(5, 4, 4, 6) + 0.1)

plot(sal_fb ~ datetime,d_all,pch=16, axes=T, ylim=c(30.5,36), cex=0.5, col="red", ylab="", xlab="", yaxt ="n", lty=1, cex.axis=1.8) +
axis(2, ylim=c(0,1),col="red",col.axis="red", las = 1,lty=1, cex.axis =1.8)

    grid(lty=1)

   par(new = T)

plot(as.Date(d_all$datetime,"%Y-%m-d %H:%M:%S", tz= "UTC"), d_all$temp_fb, col="blue", pch=16, cex=0.5, xlab="", ylab="",xaxt="n", axes=FALSE,ylim=c(-2,9))+
axis(side = 4, col="blue",col.axis="blue",las=1, cex.axis =1.8) +
mtext("Time",side=1,col="black",line=1.5, cex=1.8)
legend("topleft", legend=c("Temperature (°C)", "Salinity (PSU)"),
       col = c("blue", "red"), pch  = c(16, 16),  box.lty=0 , cex = 2)
  #grid(nx = 1, ny = NULL, col = "lightgray", lty = 1,
   #  lwd = "months")
     box()
     dev.off()

# ggsave(paste0("figures/poster_temp.png"), width= 30, height=10, poster_temp, units="cm")
# 
# poster_sal <- ggplot(data = d_all%>%dplyr::filter(sal_fb>30 ), aes(x=datetime,y=sal_fb), colour="sal_fb") +
#   geom_point(col="blue", size=0.5 )+
#   labs(x = "Time", y="Salinity (PSU)") +
#   scale_x_datetime(date_minor_breaks ="1 month")+
#   theme_bw() + theme(legend.position="bottom",legend.title = element_blank())
# print(poster_sal)
# ggsave(paste0("figures/poster_sal.png"), width= 30, height=10, poster_sal, units="cm")

@@

at_s <- ggplot(d_all_at_discrete,aes(x=sal_fb, y= at, label = month))+
  geom_text( aes(color=factor(month))) +
  scale_color_discrete(guide="none")+
    labs(x="Salinity", y="Discrete TA", color = "Months")  +
    stat_smooth(method = "lm", col = "black") +
    labs(title = paste("", "\nAdj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                       ";\nIntercept =",signif(fit$coef[[1]],5 ),
                       ";\nSlope =",signif(fit$coef[[2]], 5),
                       ";\nP =",signif(summary(fit)$coef[2,4], 5))) +
  theme_bw() + 
  theme(aspect.ratio=1,
        axis.text=element_text(size=15),
        axis.title.y= element_text(size =15),
        axis.title.x= element_text(size =15),
        plot.margin = unit(c(0.5,1,1,1), "cm"),
        plot.title = element_text(size=15, hjust=0.05,margin = margin(l = 10, b = -70))) 
  print(at_s)

ggsave(paste0("figures/Discrete_TA_salinity_AWIPEV.png"), at_s, width=15, height =11, units="cm")

@@

# #plot for POSTER june 2019
# #plot of TA calculated from S + discrete
# p_at_sal <- ggplot(data = d_all%>%dplyr::filter(at_calc > 2000), aes(x=datetime,y=at_calc,col="TA calculated from salinity") ) +
#   geom_point(col="blue", size=0.5 )+
#   geom_point(aes(y=at, fill= "Discrete measurements"), col="red") +
#   labs(title=  "Calculated TA from salinity (µmoles/kg)", x = "Time", y= "") +
#   scale_x_datetime(date_minor_breaks ="1 month")+
#   theme_bw() + theme(legend.position= c(0.7, 0.15), 
#                      legend.text=element_text(size=15),
#                      plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin(t = 10, b = -20)),
#                      axis.text=element_text(size=15),
#                      axis.title.x= element_text(size =15),
#                      legend.title=element_blank())
# 
#   
# print(p_at_sal)
# ggsave(paste0("figures/poster_at_sal.png"), width= 30, height=10, p_at_sal, units="cm")

@@

@@

#plot for POSTER june 2019
#plot of pCO2
poster_pco2 <- ggplot( ) +
  geom_point(data=d_all%>%dplyr::filter(pco2_contros > 150 & pco2_contros < 410), aes(x=datetime, y= pco2_contros,col="blue"), col="blue",size=0.5 ) +
  geom_point(data=d_all, aes(x=datetime, y=pco2calc, fill="Calculated from AT/CT"), col="red" )+
  labs(x = "Time", y ="", title = expression(~italic(p)~CO[2]~"(µatm)")) +
  theme_bw() + theme(legend.position= c(0.59, 0.1),
                     legend.text=element_text(size=14),
                     plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -30)),
                     axis.text=element_text(size=15),
                     plot.margin = unit(c(0.5,1,1,1), "cm"),
                     axis.title.x= element_text(size =15),
                     legend.title=element_blank())
print(poster_pco2)
ggsave(paste0("figures/poster_pco2.png"), width= 30, height=10, poster_pco2, units="cm")

@@

# #plot for POSTER june 2019
# #plot of pH seafet
# poster_ph <- ggplot( ) +
#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y= pHint_tot_sf,col="blue"), col="blue",size=0.5 , rm.na=TRUE) +
#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_seafet_temp_field, fill="Discrete measurements"), col="red" )+
#   labs(x = "Time", y ="", title = expression(pH[T]~seaFET)) +
#   theme_bw() + theme(legend.position= c(0.8, 0.1), 
#                      legend.text=element_text(size=14),
#                       plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -35)),
#                       axis.text=element_text(size=15),
#                       plot.margin = unit(c(1,1,1,1), "cm"),
#                       axis.title.x= element_text(size =15),
#                       legend.title=element_blank())
# 
# print(poster_ph)
# ggsave(paste0("figures/poster_ph.png"), width= 30, height=10, poster_ph, units="cm")
# 
# # RANGE of pH
# d_all<- d_all%>%
#   dplyr::mutate(year = year(datetime))
# range <- tbl_df(
#   d_all %>%
#   group_by(date=as.Date(datetime), month=month(datetime, label=TRUE), year=year(datetime)) %>%
#   summarize(pH_range = max(pHint_tot_sf) - min(pHint_tot_sf))
# )
# quant <- quantile(range$pH_range, probs =c(2.5/100, 97.5/100), na.rm =TRUE)
# 
# # Per month
# range_month <-
#   range %>%
#   group_by(Month = month(date, label=TRUE, abbr=FALSE)) %>%
#   summarize(pH_range_month = mean(pH_range, na.rm=TRUE))
# 
# size_point <- 0.4 # size of data points
# plot_range_sf <-  
#   ggplot(data=range, aes(x = as.factor(month), y = pH_range)) +
#   geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
#   geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
#   labs(y =expression(paste(pH[T], " range seaFET")), x=NULL, title=NULL) +
#   Mytheme() +
#   theme(panel.grid.major.x = element_blank())
# print(plot_range_sf)
# ggsave(paste0("figures/plot_range_sf.png"), width= 30, height=10, plot_range_sf, units="cm")

@@

# #plot for POSTER june 2019
# #plot of pH durafet
# poster_dur <- ggplot( ) +
#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y= pH_durafet_corrected,col="blue"), col="blue",size=0.5 , rm.na=TRUE) +
#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_durafet_temp_field, fill="Discrete measurements"), col="red" )+
#   labs(x = "Time", y= "", title = expression(pH[T]~durafet)) +
#   theme_bw() + theme(legend.position= c(0.7, 0.8), 
#                      legend.text=element_text(size=14),
#                       plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -35)),
#                       axis.text=element_text(size=15),
#                       plot.margin = unit(c(1,1,1,1), "cm"),
#                       axis.title.x= element_text(size =15),
#                       legend.title=element_blank())
# 
# print(poster_dur)
# ggsave(paste0("figures/poster_dur.png"), width= 30, height=10, poster_dur, units="cm")
# 
# # RANGE of pH
# range_dur <- tbl_df(
#   d_all %>%
#   group_by(date=as.Date(datetime), month=month(datetime, label=TRUE), year=year(datetime)) %>%
#   summarize(pH_range = max(pH_durafet_corrected) - min(pH_durafet_corrected))
# )
# quant <- quantile(range_dur$pH_range, probs =c(2.5/100, 97.5/100), na.rm =TRUE)
# 
# # Per month
# range_month <-
#   range_dur %>%
#   group_by(Month = month(date, label=TRUE, abbr=FALSE)) %>%
#   summarize(pH_range_month = mean(pH_range, na.rm=TRUE))
# 
# size_point <- 0.4 # size of data points
# plot_range_dur <-  
#   ggplot(data=range_dur, aes(x = as.factor(month), y = pH_range)) +
#   geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
#   geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
#   labs(y =expression(paste(pH[T], " range durafet")), x=NULL, title=NULL) +
#   Mytheme() +
#   theme(panel.grid.major.x = element_blank())
# print(plot_range_dur)
# ggsave(paste0("figures/plot_range_dur.png"), width= 30, height=10, plot_range_dur, units="cm")
```
The average offset between durafet and references (spectro) data is `r average_offset_dur` pH unit (sd = `r sd_offset_dur`, n = `r n_offset_dur`).
